---
title: " Cars Prediction"
author: "Gherardo Lattanzi"
date: "2016-08-15"
output: html_document
---

The Following is the initial dataset given for this Report. 50 Observations with 2 attributes each. 
```{r pressure, echo = TRUE}
cars<- read.csv("~/Desktop/Ubiqum/Task2/cars.csv")
knitr::kable(cars, align = "c")
```



## DATA CLEANING
For the data cleaning work, the names of the colums are now in a technically correct form.
Moreover, a new column called squared speed is created in order to spot the outliers.

### Create Squared Speed Column
```{r}
names(cars) <-c("name.of.car","speed.of.car", "distance.of.car")
cars$squared.speed <- cars$speed.of.car*cars$speed.of.car

```

### Identify and Eliminate Outliers
```{r}
boxplot(cars$distance.of.car, cars$speed.of.car)

outliers <- boxplot(cars$distance.of.car, plot=FALSE)$out
show(outliers)

###Outliers removed
cars <- cars[-which(cars$distance.of.car %in% outliers),]
```

### Training and Testing TestSets
```{r}
trainSize<-round(nrow(cars)*0.7) 
print(trainSize)
testSize<-nrow(cars)-trainSize
print(testSize)
```

```{r}
training_indices<-sample(seq_len(nrow(cars)),size =trainSize)
trainSet<-cars[training_indices,]
testSet<-cars[-training_indices,] 
print(testSet)
```


### LINEAR REGRESSION
```{r include=FALSE}
MOD <- lm(distance.of.car ~ speed.of.car, trainSet)
summary(MOD)

coefficients(MOD)

COEFF.INTERCEPT <- coefficients(MOD)[1]
COEFF.SLOPE <- coefficients(MOD)[2]


```
###Prediction
```{r}
Prediction<- predict(MOD,testSet)

knitr::kable(Prediction)
```

```{r cars, echo=FALSE}
plot(cars$distance.of.car, cars$Squared.Speed)
```

### GRAPHIC Distance and Squared Speed
```{r eval=FALSE, include=FALSE}

library(ggplot2)
speed.of.car2 <- testSet$Squared.Speed
ggplot(testSet,
       aes(x = Squared.Speed, y = distance.of.car)) + 
  geom_point(color = "blue") +
 geom_abline(intercept = COEFF.INTERCEPT1, slope = COEFF.SLOPE1) + 
ggtitle("Better fit of the Regression")


```

